New insights into the Weddell Sea ecosystem applying a network approach

### 2022-11-07 Manuscript/Manuscript.Rmd
Updating Results

This marine food web compiles all the food web data available for the high Antarctic Weddell Sea collected since 1983, and is one of the most highly-resolved marine food webs documented to date. It's noteworthy that it is a summary network that ignores seasonal changes [@Jacob2011].

@@

We analysed the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) studying the properties of the species in a network approach; and c) comparing the stability of the food web after performing species extinction simulations.

@@

To estimate the strength of each interaction in the food web, we followed the methodology proposed by @Pawar2012. The minimum data requirements are: body mass of the consumer (predator) and resource (prey), and the interaction dimensionality classified as 2 or 3 dimensions. GATEWAy v.1.0 does provide the mean mass for consumers and resources (except for 'detritus' and 'sediment') and the dimensionality for every interaction, though the latter is missing for 924 interactions. To solve this issue, we used information about movement type for consumer and resource included in GATEWAy. Then, we classified the interaction as 2D if both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource). The interaction was classified as 3D if both consumer and resource move in 3D (e.g., both swimming) or if the consumer moves in 2D and the resource in 3D (e.g., sessile/walking consumer, swimming resource) [@Pawar2012].

@@

We obtained estimations for the resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively [@Pawar2012]. The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality. On one hand, resource density scales with resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources 'phytodetritus' and 'sediment' were not available in GATEWAy, we considered the body mass of the smallest phytoplankton species ('Fragilariopsis cylindrus') as a proxy. This is justified by the fact that 'phytodetritus' and 'sediment' are mainly composed by dead or senescent phytoplankton reaching the seabed (@Wolanski2011). On the other hand, search rate scales with consumer mass as a power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.

After this, we fit the interaction strength distribution of the food web considering six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion AIC [@Burnham2002].

@@

In order to individually characterize the species of the food web, we considered weighted and unweighted properties (Figure 2). The former is based on the estimation of the interaction strength described in the previous section. The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014].

As the weighted property we took into account the mean interaction strength, meaning the average strength of all species' interactions. On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, taking into account in- and out-coming interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers. The following are arguments to have selected the above properties. The degree has often been equated with importance to the structure and functioning of a community, i.e. perturbations to high-degree species may therefore have larger effects on the food web than perturbations to low-degree species [@Dunne2002a; references in @Cirtwill2018a]. The trophic level offers information about how important a species is to its biotic community, i.e. top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a]. The trophic similarity measures the similarity of one of the most important aspect of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].

Furthermore, we took into account the species' habitat, which describes the physical position of a species within the environment. These data was taken from @Jacob2011. Species were categorized as: 1) benthic, if the species lives on the seafloor; 2) pelagic, if the species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not aquatic but feeds predominantly in the marine realm.

With the aim of studying the relationship between the interaction strength of the species and its unweighted properties and habitat, we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties.

>>>>

This marine food web compiles all the trophic data available for the high Antarctic Weddell Sea collected since 1983, and is one of the most highly-resolved marine food webs documented to date. It's noteworthy that it is a summary network that ignores seasonal changes [@Jacob2011].

@@

We analysed the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) studying the species properties in a network framework; and c) comparing the stability of the food web after performing species extinction in silico simulations.

@@

To estimate the strength of each interaction in the food web we followed the methodology proposed by @Pawar2012. The minimum data requirements are: body mass of the consumer (predator) and resource (prey), and the interaction dimensionality classified as 2 or 3 dimensions. GATEWAy v.1.0 does provide the mean mass for consumers and resources (except for 'detritus' and 'sediment') and the dimensionality for the majority of the interactions, though the latter is missing in some cases (924 interactions). To complete such missing data, we used information about movement type for consumer and resource included in GATEWAy. Thus, we classified the interaction as 2D if both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource). The interaction was classified as 3D if both consumer and resource move in 3D (e.g., both swimming) or if the consumer moves in 2D and the resource in 3D (e.g., sessile/walking consumer, swimming resource) [@Pawar2012].

@@

We obtained estimations for the resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively [@Pawar2012]. The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality. On one hand, resource density scales with resource mass as power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources 'phytodetritus' and 'sediment' were not available in GATEWAy, we considered the body mass of the smallest phytoplankton species ('Fragilariopsis cylindrus') as a proxy. This is justified by the fact that 'phytodetritus' and 'sediment' are mainly composed by dead or senescent phytoplankton reaching the seabed (@Wolanski2011). On the other hand, search rate scales with consumer mass as power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.

Finally, we fit the interaction strength distribution of the food web considering six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion AIC [@Burnham2002].

@@

In order to individually characterize the species of the food web, we considered weighted and unweighted properties (Figure 2). The former is based on the estimation of the interaction strength described in the previous section. The latter is related to properties commonly used in qualitative or topological (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014].

As the weighted property we took into account the total mean interaction strength, meaning the average strength of all species' interactions for each species. On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, summing up in- and out-coming interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap based on shared and unique resources and consumers. The following are arguments to have selected the unweighted properties. The degree has often been equated with importance to the structure and functioning of a community, i.e. perturbations to high-degree species may therefore have larger effects on the food web than perturbations to low-degree species [@Dunne2002a; references in @Cirtwill2018a]. The trophic level offers information about how important a species is to its biotic community, i.e. top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a]. The trophic similarity measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].

Furthermore, we took into account the species' habitat, which describes the physical position of a species within the ecosystem. Species were categorized as: 1) benthic, if the species lives on the seafloor; 2) pelagic, if the species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not aquatic but feeds predominantly in the marine realm. These data was taken from @Jacob2011.

With the aim of studying the relationship between the interaction strength of the species (weighted property) and its unweighted properties we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties. We also explored such weighted property with species habitat.

### 2022-11-07 Manuscript/Manuscript.tex
Updating Results

Regarding the distribution of the species' mean interaction strength and
its relationship with the unweighted properties, we found that
interaction strength-trophic level showed the strongest linear
regression: the higher the trophic level of the species, the higher its
mean interaction strength. We also found a positive relationship with
the degree (total number of interactions). On the other hand, CONTINUE
HERE \ldots{}

The so-called `High IS' and `Low IS' groups of species exhibited
different and, in some cases, opposite relationships with unweighted
properties. It's noteworthy that only the relationship with trophic
level revealed a similar trend in the regression analysis for both
groups: mean interaction strength increases with trophic level (Figure
5A). On the contrary, the linear regressions with degree and trophic
similarity showed opposite relationships comparing groups. These mean
that in species with relatively higher mean interaction strength, `High
IS', such strength decreases when the number of interactions (degree)
increases; the opposite occurs in species with relatively lower
interaction strength `Low IS' (Figure 5B). Regarding trophic similarity,
the interaction strength decreases in `High IS' species while increases
in `Low IS' species (Figure 5C).

>>>>

Regarding the distribution of the species' mean interaction strength and
its relationship with the unweighted properties (Figure 4), we found
that interaction strength-trophic level showed the strongest linear
regression: the higher the trophic level of the species, the higher its
mean interaction strength. We also found a positive relationship with
the degree (total number of interactions). On the other hand, there was
no evident relationship with trophic similarity. Considering species
habitat, the ``Benthopelagic'' and ``Pelagic'' categories presented the
two species with the highest mean interaction strength, though
``Demersal'' and ``Land-based'' concentrated the majority of the species
with relatively higher interaction strength. Species inhabiting the
benthic realm showed the lowest mean interaction strength (Figure 4D).

CONTINUE MODIFYING HERE: The so-called `High IS' and `Low IS' groups of
species exhibited different and, in some cases, opposite relationships
with unweighted properties. It's noteworthy that only the relationship
with trophic level revealed a similar trend in the regression analysis
for both groups: mean interaction strength increases with trophic level
(Figure 5A). On the contrary, the linear regressions with degree and
trophic similarity showed opposite relationships comparing groups. These
mean that in species with relatively higher mean interaction strength,
`High IS', such strength decreases when the number of interactions
(degree) increases; the opposite occurs in species with relatively lower
interaction strength `Low IS' (Figure 5B). Regarding trophic similarity,
the interaction strength decreases in `High IS' species while increases
in `Low IS' species (Figure 5C).
